Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-09-19 documents/TriangleScenarioArXiv/ts.tex
typo

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In structures where all parties share a common resource, these non-classical correlations are also known as non-local correlations. Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. This provides the first robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    \Cref{sec:causal_compatibility} introduced the notion of causal compatibility inequalities, and \cref{sec:fritz_distribution} discussed the Fritz distribution ($\prob[\fritz]$) together with the initial inequality-free proof of its incompatibility with the Triangle structure. Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution. A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq_symplified}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tfraser@perimeterinstitute.ca}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In structures where all parties share a common resource, these non-classical correlations are also known as non-local correlations. Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. This provides the first robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    \Cref{sec:causal_compatibility} introduced the notion of causal compatibility inequalities, and \cref{sec:fritz_distribution} discussed the Fritz distribution ($\prob[\fritz]$) together with the initial inequality-free proof of its incompatibility with the Triangle structure. Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution. A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
